---
title: "Pokemon Analysis"
format: pdf
---
```{r}
library(ggplot2)
library(dplyr)

library(mltools)
library(data.table)
library(car)
```

The professor recommended doing this so the empty string "" will be converted to a NA value so we can then use the is.na() function. 
```{r}
pokemon <- read.csv("/Users/sarah/Desktop/SDS291/FinalProject/pokemon.csv", na.strings = c(NA, ""))
```

Making the dual_type column that says if the Pokemon is a dual type based on if there is a second type. 
```{r}
pokemon <- mutate(pokemon, dual_type = !is.na(type2))
```

```{r}
pokemon$'capture_rate' = as.numeric(pokemon$'capture_rate')
pokemon$'type1' = as.factor(pokemon$'type1')
pokemon$'type2' = as.factor(pokemon$'type2')
```

# Removing legendaries and making pokemone2 dataset
```{r}
pokemon2 <- filter(pokemon, is_legendary == 0)
```

# Making sure that these variables are the right data type (specifically making sure capture rate is numeric)
```{r}
pokemon2$'capture_rate' = as.numeric(pokemon2$'capture_rate')
pokemon2$'type1' = as.factor(pokemon2$'type1')
pokemon2$'type2' = as.factor(pokemon2$'type2')
```


# parts i will be focusing on 
## visualizations 
### hp and capture_rate 
```{r}
  ggplot(data = pokemon2, mapping = aes(x = hp, y = capture_rate)) +
    geom_point() +
    geom_smooth(method = lm, se = FALSE, formula = y~x) + 
    xlab("Hit Points") +  
    ylab("Capture Rate") + 
    ggtitle("Hit Points vs Capture Rate")
```

### defense and capture_rate
```{r}
  ggplot(data = pokemon2, mapping = aes(x = defense, y = capture_rate)) +
    geom_point() +
    geom_smooth(method = lm, se = FALSE, formula = y~x) + 
    xlab("Defense") + 
    ylab("Capture Rate") + 
    ggtitle("Defense vs Capture Rate")
```

### speed and capture_rate 
```{r}
  ggplot(data = pokemon2, mapping = aes(x = speed, y = capture_rate)) +
    geom_point() +
    geom_smooth(method = lm, se = FALSE, formula = y~x) + 
    xlab("Speed") + 
    ylab("Capture Rate") + 
    ggtitle("Speed vs Capture Rate")
```

